\documentclass{ximera}

\input{../preamble.tex}

\title{Definition of the derivative}

\begin{document}

\begin{abstract}
%Stuff can go here later if we want!
\end{abstract}

\maketitle

\begin{sectionOutcomes}

After completing this section, students should be able to do the following.

\begin{itemize}
\item Use limits to find the slope of the tangent line at a point.
\item Understand the definition of the derivative at a point.
\item Compute the derivative of a function at a point.
\item Estimate the slope of the tangent line graphically.
\item Write the equation of the tangent line to a graph at a given point.
\item Recognize and distinguish between secant and tangent lines.
\item Recognize different notation for the derivative.
\item Recognize the the tangent line as a local approximation for a
  differentiable function.
\end{itemize}

\end{sectionOutcomes}

\bigskip

%---Prereq notes/links----------%
\textbf{Skills you may want to brush up on first}: To be ready to work
through these lessons, you may need to review the following trigonometry and algebra topics.
\begin{itemize}
    \item \link[Polynomial functions]{https://ximera.osu.edu/course/ColoradoStateMath/Math160Prerequisite/master/reviewOfFamousFunctions/digInPolynomialFunctions} and point slope form%%
    \item \link[Factoring]{https://ximera.osu.edu/course/ColoradoStateMath/Math160Prerequisite/master/prerequisiteVideos/fundamentalsOfFactoring}
    \item When to add 0 or multiply by 1.
\end{itemize}

\bigskip

\textbf{Warning}: If you are in canvas and you click on the links above, they will redirect you
to the Algebra and Trigonometry page in Ximera. You will need to
go into your 'modules' page and go back into the Exam 1 pages again
when you feel you are ready to move to the Calculus course content.


\end{document}
