\documentclass{ximera}

\input{../preamble.tex}

\title{Product rule and quotient rule}

\begin{document}

\begin{abstract}
%Stuff can go here later if we want!
\end{abstract}

\maketitle

\begin{sectionOutcomes}

After completing this section, students should be able to do the following.

\begin{itemize}
	\item Identify products of functions.
	\item Use the product rule to calculate derivatives.
	\item Identify quotients of functions.
	\item Use the quotient rule to calculate derivatives.
	\item Combine derivative rules to take derivatives of more complicated functions.
        \item Explain the signs of the terms in the numerator of the quotient rule.
        \item Multiply tangent lines to justify the product rule.
	\item Use the product and quotient rule to calculate derivatives from a table of values.
\end{itemize}

\end{sectionOutcomes}

\bigskip

%---Prereq notes/links----------%
\textbf{Skills you may want to brush up on first}: To be ready to work
through these lessons, you may need to review the following trigonometry and algebra topics.
\begin{itemize}
    \item \link[Functions]{https://ximera.osu.edu/course/ColoradoStateMath/Math160Prerequisite/master/understandingFunctions/titlePage}
    \item \link[Polynomials]{https://ximera.osu.edu/course/ColoradoStateMath/Math160Prerequisite/master/reviewOfFamousFunctions/digInPolynomialFunctions}
    \item \link[Trigonometric functions]{https://ximera.osu.edu/course/ColoradoStateMath/Math160Prerequisite/master/reviewOfFamousFunctions/digInTrigonometricFunctions}
    \item Products \& quotients
\end{itemize}

\bigskip

\textbf{Warning}: If you are in canvas and you click on the links above, they will redirect you
to the Algebra and Trigonometry page in Ximera. You will need to
go into your 'modules' page and go back into the Exam 1 pages again
when you feel you are ready to move to the Calculus course content.



\end{document}
