\documentclass{ximera}

\input{../preamble.tex}

\title{Derivatives as functions}

\begin{document}

\begin{abstract}
%Stuff can go here later if we want!
\end{abstract}

\maketitle

\begin{sectionOutcomes}

After completing this section, students should be able to do the following.

\begin{itemize}
\item Understand the derivative as a function related to the original
  definition of a function.
\item Find the derivative function using the limit definition.
\item Relate the derivative function to the derivative at a point.
\item Explain the relationship between differentiability and continuity.
\item Relate the graph of the function to the graph of its derivative.
\item Determine whether a piecewise function is differentiable.
\end{itemize}

\end{sectionOutcomes}
\bigskip

%---Prereq notes/links----------%
\textbf{Skills you may want to brush up on first}: To be ready to work
through these lessons, you may need to review the following trigonometry and algebra topics.
\begin{itemize}
    \item \link[Functions]{https://ximera.osu.edu/course/ColoradoStateMath/Math160Prerequisite/master/understandingFunctions/titlePage}
    \item \link[Function notation]{https://ximera.osu.edu/course/ColoradoStateMath/Math160Prerequisite/master/prerequisiteVideos/functionNotation}
    \item \link[Graphing]{https://ximera.osu.edu/course/ColoradoStateMath/Math160Prerequisite/master/prerequisiteVideos/functionsAndTheirGraphs}
    \item Piece-wise functions
\end{itemize}

\bigskip

\textbf{Warning}: If you are in canvas and you click on the links above, they will redirect you
to the Algebra and Trigonometry page in Ximera. You will need to
go into your 'modules' page and go back into the Exam 1 pages again
when you feel you are ready to move to the Calculus course content.


\end{document}
