\documentclass{ximera}

\input{../preamble.tex}

\title{Rules of differentiation}

\begin{document}

\begin{abstract}
%Stuff can go here later if we want!
\end{abstract}

\maketitle

\begin{sectionOutcomes}

After completing this section, students should be able to do the following.

\begin{itemize}
	\item Use the definition of the derivative to develop shortcut rules to find the derivatives of constants and constant multiples.
	\item Use the definition of the derivative to develop shortcut rules to find the derivatives of powers of $x$.
	\item Use the definition of the derivative to develop shortcut rules to find the derivatives of sums and differences of functions.
        \item Compute the derivative of polynomials.
        %\item State the derivative of the natural exponential function.
	\item State the derivative of the sine function.
\end{itemize}

\end{sectionOutcomes}

\bigskip

%---Prereq notes/links----------%
\textbf{Skills you may want to brush up on first}: To be ready to work
through these lessons, you may need to review the following trigonometry and algebra topics.
\begin{itemize}
    \item \link[Functions]{https://ximera.osu.edu/course/ColoradoStateMath/Math160Prerequisite/master/understandingFunctions/titlePage}
    \item \link[Polynomials]{https://ximera.osu.edu/course/ColoradoStateMath/Math160Prerequisite/master/reviewOfFamousFunctions/digInPolynomialFunctions}
\end{itemize}

\bigskip

\textbf{Warning}: If you are in canvas and you click on the links above, they will redirect you
to the Algebra and Trigonometry page in Ximera. You will need to
go into your 'modules' page and go back into the Exam 1 pages again
when you feel you are ready to move to the Calculus course content.


\end{document}
